\documentclass{article}
\usepackage{bubblecv}

\begin{document}


\begin{cv}[avatar]{Hafsa Abdi}{Data Analyst}


\cvsection[summary]{Profile}  %-----------------------------------------------------------

I’m a dedicated and driven student with coding experience in Python, Java, HTML, and CSS. I consistently strive for excellence in my academics and I am always willing to learn new skills. I am friendly, a good communicator and able to work in both independent and group settings.

\cvsection[work]{Work experience}  %------------------------------------------------------

\begin{cvevent}[2024][present]
    \cvname{Intern/Trainee}
    \cvdescription{PwC, London}
    \begin{itemize}
        \item Covert intelligence operations for national security.
        \item Infiltration from high-risk environments.
        \item Utilization of advanced espionage techniques and gadgets.
        \item Surveillance, analysis, and threat prevention.
    \end{itemize}
\end{cvevent}


\cvsection[education]{Education}  %------------------------------------------------------

\begin{cvevent}[2024][present]
    \cvname{Student}
    \cvdescription{Queen Mary University, London}
    \textbf{Courses and Achievements:}
    \begin{itemize}
        \item Mastered advanced techniques for discreetly gathering intelligence and conducting covert operations.
        \item Trained extensively in planning and executing covert operations and infiltrating high-security areas.
        \item Received rigorous combat training in martial arts, firearms handling, and tactical skills.
        \item Proficient in surveillance methods, counter-surveillance techniques, and analyzing gathered intelligence.
    \end{itemize}
\end{cvevent}

\begin{cvevent}[2022][2024]
    \cvname{Student}
    \cvdescription{Chelsea Academy, London}

    \begin{itemize}
        \item Achieved A*AA in Alevels in Maths, Chemistry, Biology.  

    \end{itemize}
\end{cvevent}

\begin{cvevent}[2017][2022]
    \cvname{Student}
    \cvdescription{Madani Girls' Secondary School, London}

    \begin{itemize}
        \item Achieved 9-8 in Combined Science, 8 in Math, 7 in English Language and 7 in Computer Science. 

    \end{itemize}
\end{cvevent}


\cvsection[target]{Certifications}  %----------------------------------------------------------

\begin{cvevent}[2002]
    \cvname{Die Another Day}
    Uncovered a North Korean general's plan to use a satellite weapon to create a war between North and South Korea.
\end{cvevent}

\cvseparator[2]
\begin{cvevent}[1999]
    \cvname{The World Is Not Enough}
    Protected an oil heiress from a terrorist plotting to exploit her family's resources and trigger a global meltdown.
\end{cvevent}

\cvseparator[2]
\begin{cvevent}[1997]
    \cvname{Tomorrow Never Dies}
    Investigated a media mogul's plot to provoke a war between the UK and China for increased ratings and power.
\end{cvevent}

\cvseparator[2]
\begin{cvevent}[1995]
    \cvname{GoldenEye}
    Prevented the use of the GoldenEye satellite weapon system by a rogue agent to cause global financial chaos.
\end{cvevent}


\cvsidebar %-----------------------------------------------------------------------------


\cvsection[contact]{Contact}  %----------------------------------------------------------

\begin{cvitem}[Envelope][4]
    \textbf{Email}\\
    \href{mailto:james.bond@mi6.gov}{\texttt{hafsaabdifitah06@gmail.com}}
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Phone][4]
    \textbf{Phone}\\
    \href{tel:+442071234567}{\texttt{+44 7360 217402}}
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Home][4]
    \textbf{Address}\\
     London, United Kingdom
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Globe][4]
    \textbf{GitHub}\\
    \href{https://www.mi6.gov.uk}{\texttt{https://github.com/hafybufya}}
\end{cvitem}


\cvsection[skills]{Skills}  %-----------------------------------------------------------

\begin{cvitem}
    Espionage Techniques
\end{cvitem}

\cvseparator
\begin{cvitem}
    Surveillance
\end{cvitem}

\cvseparator
\begin{cvitem}
    Combat Training
\end{cvitem}

\cvseparator
\begin{cvitem}
    Infiltration
\end{cvitem}

\cvseparator
\begin{cvitem}
    Problem Solving
\end{cvitem}

\cvseparator
\begin{cvitem}
    Effective Communication
\end{cvitem}

\cvseparator
\begin{cvitem}
    Adaptability
\end{cvitem}

\cvseparator
\begin{cvitem}
    Teamwork
\end{cvitem}






\end{document}
